Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-13 paper/ijcai/paper.tex
polishing

\begin{table*}[h]
	\centering
	\begin{tabular}{@{}llll@{}}
\toprule
  & SFL                    & \comb{}-5                 & \comb{}-10                 \\ \midrule
Mean & 387.46     & 576.74   & 522.35   \\ \midrule
Median & 44.50      & 48.25               & 46.00                \\ \midrule
Variance & 827.80      & 1075.90   & 1275.34    \\ \midrule
Shapiro-Wilk & \makecell{W = 0.51 \\ p-value = 9.65 x $10^{-21}$} & \makecell{W = 0.59 \\ p-value = 5.29 x $10^{-19}$} & \makecell{W = 0.56 \\ p-value = 8.95 x $10^{-20}$}  \\ \midrule
Friedman & \multicolumn{3}{c}{\makecell{$\chi^{2}$ = 16.87 \\ p-value = 2.2 x $10^{-4}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests \Sof{Considering \chart{}, \jtime{}, \mockito{}, \lang{} }}
  \label{table:st}
\end{table*}

>>>>

\begin{table*}[h]
	\centering
	\begin{tabular}{@{}llll@{}}
\toprule
  & SFL                    & \combpar{5}                 & \combpar{10}                 \\ \midrule
Mean & 387.46     & 576.74   & 522.35   \\ \midrule
Median & 44.50      & 48.25               & 46.00                \\ \midrule
Variance & 827.80      & 1075.90   & 1275.34    \\ \midrule
Shapiro-Wilk & \makecell{W = 0.51 \\ p-value = 9.65 x $10^{-21}$} & \makecell{W = 0.59 \\ p-value = 5.29 x $10^{-19}$} & \makecell{W = 0.56 \\ p-value = 8.95 x $10^{-20}$}  \\ \midrule
Friedman & \multicolumn{3}{c}{\makecell{$\chi^{2}$ = 16.87 \\ p-value = 2.2 x $10^{-4}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests \Sof{Considering \chart{}, \jtime{}, \mockito{}, \lang{} }}
  \label{table:st}
\end{table*}
